\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
\fontdir[fonts/]
\colorlet{awesome}{awesome-red}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%       CJK (Chinese/Japanese/Korean) Font Support
%-------------------------------------------------------------------------------
% Add Chinese font support using xeCJK
\usepackage{xeCJK}
% Set Chinese fonts (fallback to available system fonts)
\setCJKmainfont{Droid Sans Fallback}
\setCJKsansfont{Droid Sans Fallback}
\setCJKmonofont{Droid Sans Fallback}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
\name{E**}{-}
\position{Python}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {E** -~~~\textperiodcentered~~~Résumé}
  {\thepage}

%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%-------------------------------------------------------------------------------
\cvsection{Summary}
\begin{cvitems}  \item {Currently pursuing a Master's degree in Computer Science and Technology. Passionate about exploring new technologies, familiar with common programming languages such as Java, Python, C++, etc. Passed English CET-6, capable of reading general English literature. Understand basic knowledge of deep learning, completed CNN, RNN and other networks based on Tensorflow.}  \item {Desired Position: Python @ Nanjing, 30-35K}  \item {Desired Position: Golang @ Nanjing, 30-35K}  \item {Desired Position: Java @ Nanjing, 30-35K}\end{cvitems}


\cvsection{Professional Experience}
\begin{cventries}  \cventry
    {Java}
  {Alibaba (Beijing) Software Services Co., Ltd.}
    {None}
    {2022.06 - Present}
    {      \begin{cvitems}        \item {1. Model Data Management Service Development}        \item {1.1 Python SDK Development.}        \item {1.2 Model Data Reclamation Strategy Development.}        \item {1.3 Model Metric Collection.}        \item {2. Developed Python SDK for internal distributed file system based on Ctypes.}        \item {3. AI Platform Training Scheduling Control System Development}        \item {3.1 Supported automatic task scaling.}        \item {3.2 Multi-priority system, supporting Min-Max guarantee and high-priority preemption.}        \item {3.3 Task status display, log display, training progress, etc.}      \end{cvitems}    }  \cventry
    {Backend Development}
  {Alibaba (China) Co., Ltd.}
    {None}
    {2021.05 - Present}
    {      \begin{cvitems}        \item {Participated in feature center development based on Java, MySQL, Flink. Main work includes:}        \item {Responsible for development of sample feature meta-information management function, unifying management of feature meta-information scattered in different modules and providing external interfaces.}        \item {Responsible for development of real-time sample production intermediate result preview function, tailoring sample production process according to frontend configuration and outputting sample production information, effectively improving algorithm colleagues' independent iteration ability.}      \end{cvitems}    }  \cventry
    {Python}
  {Baidu Online Network Technology (Beijing) Co., Ltd.}
    {None}
    {2020.12 - 2021.03}
    {      \begin{cvitems}        \item {Internship Project: Baidu Maps Recommendation Card Header Image Optimization. Main work includes:}        \item {Used company image feature operators to batch calculate features of tens of millions of images, and iterated image optimization strategy based on image features; executed optimization strategy based on Hadoop streaming, the strategy has been launched, and image aesthetic evaluation received a 15\% increase; perfected image optimization routine process, implementing automated optimization of incremental images.}        \item {Developed image selection web tool based on Python, Flask, Javascript, Docker. Main functions include image feature evaluation, optimization result SGB evaluation (supporting CSV table generation), improving the evaluation process of optimization strategy and accelerating strategy iteration.}      \end{cvitems}    }  \cventry
    {Python}
  {Beijing ByteDance Technology Co., Ltd.}
    {None}
    {2020.06 - 2020.08}
    {      \begin{cvitems}        \item {Participated in company recommendation system platform development based on Flask, Vue, MySQL, etc. Main work includes:}        \item {Implemented platform model tagging function (search models by tag name). Designed and extended original database according to functional requirements; wrote backend logic to provide RESTful interfaces; wrote frontend pages to call interfaces to complete CRUD of model tags.}        \item {Implemented platform model jump AB experiment function. Designed database according to functional requirements; wrote model AB information pre-filling and jump experiment platform RESTful interfaces; wrote frontend pages to call interfaces to implement functions.}      \end{cvitems}    }\end{cventries}


\cvsection{Projects}
\begin{cventries}  \cventry
    {Main Person in Charge}
  {After-school Q&A System}
    {None}
    {2017.06 - 2018.06}
    {      \begin{cvitems}        \item {Implemented Q&A system based on Django, Jquery, Bootstrap, MySQL, etc. Main responsibilities:}        \item {Frontend page design and implementation of online Q&A module;}        \item {Wrote backend logic, implementing functions such as asking questions, answering questions, commenting, collecting questions, inviting answers, etc.}      \end{cvitems}    }\end{cventries}


\cvsection{Education}
\begin{cventries}  \cventry
    {Master}
  {Beijing University of Posts and Telecommunications}
    {None}
    {2019 - 2022}
    {      \begin{cvitems}        \item {Major: Computer Science and Technology}      \end{cvitems}    }  \cventry
    {Bachelor}
  {Nanjing University of Posts and Telecommunications}
    {None}
    {2015 - 2019}
    {      \begin{cvitems}        \item {Major: Computer Science and Technology}      \end{cvitems}    }\end{cventries}


%-------------------------------------------------------------------------------
\end{document}
