\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}
\fontdir[fonts/]
\colorlet{awesome}{awesome-red}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

%-------------------------------------------------------------------------------
%       CJK (Chinese/Japanese/Korean) Font Support
%-------------------------------------------------------------------------------
% Add Chinese font support using xeCJK
\usepackage{xeCJK}
% Set Chinese fonts (fallback to available system fonts)
\setCJKmainfont{Droid Sans Fallback}
\setCJKsansfont{Droid Sans Fallback}
\setCJKmonofont{Droid Sans Fallback}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
\name{Xu**}{-}
\position{Large Model Algorithms}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {Xu** -~~~\textperiodcentered~~~Résumé}
  {\thepage}

%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%-------------------------------------------------------------------------------
\cvsection{Summary}
\begin{cvitems}  \item {Focusing on intelligence in dev infra domain. Familiar with LLM applications, agents, AIOps, and database platforms.}  \item {Desired Position: LLM Algorithms @ Nanjing, 70-100K}  \item {Desired Position: LLM Algorithms @ Shanghai, 90-120K}  \item {Desired Position: LLM Algorithms @ Hangzhou, 80-110K}\end{cvitems}


\cvsection{Professional Experience}
\begin{cventries}  \cventry
    {Senior Algorithm Expert}
  {Beijing ByteDance Technology Co., Ltd.}
    {None}
    {2024.04 - Present}
    {      \begin{cvitems}        \item {LLM applications, agents, Doubao}      \end{cvitems}    }  \cventry
    {Algorithm Expert}
  {Beijing Sankuai Online Technology Co., Ltd.}
    {None}
    {2021.08 - Present}
    {      \begin{cvitems}        \item {Database autonomy, LLM applications}      \end{cvitems}    }  \cventry
    {Algorithm Engineer}
  {Huawei}
    {None}
    {2017.04 - 2021.08}
    {      \begin{cvitems}        \item {Engaged in research and implementation of algorithms related to AIOps, advertising, and user experience, including:}        \item {Metric Anomaly Detection: Using time series processing, IForest, probability distribution modeling and other algorithms, based on time series features, built anomaly detection capabilities to support minute-level real-time anomaly detection for millions of KPIs on the live network, providing quality assurance for 100+ services of Huawei Consumer Cloud Services.}        \item {Advertising Audience Expansion: Based on GBDT for feature selection, using LR/Linear SVM for classification modeling, expanded similar audiences for advertisers' selected audiences to improve conversion effects, increasing conversion rate by 200\%+ in 1:1 diffusion.}        \item {Advertising Fault Localization: Based on advertising business processes and metric correlations, using MDRCA, comparative analysis, change correlation and other operators, built intelligent fault localization capabilities for advertising business, supporting flowchart injection and online learning of expert experience. The accuracy rate is 70\%+, deployed in 2 businesses.}        \item {Public Opinion Monitoring: Using BERT algorithm to perform NLP classification and tagging on user public opinion data from APP feedback, telephone work orders, and the Internet. Real-time detection based on tagged data to discover public opinion issues; mining hot topics to track public opinion issues; covering 10+ APPs.}        \item {Grayscale Assessment: Using distribution modeling and hypothesis testing methods, performed grayscale-live comparison scoring on indicators such as user experience, core interface success rate, and machine load during the grayscale launch process, and drilled down into problem indicators to give root causes. Accessed by 10+ cloud service businesses.}        \item {User Experience Analysis: Based on user questionnaires, analyzed the relationship and weight between various business indicators and NPS, providing direction and priority suggestions for product improvement, deployed in 2 cloud service businesses.}      \end{cvitems}    }  \cventry
    {Algorithm Engineer}
  {China UnionPay Technology Development Center}
    {None}
    {2016.07 - 2016.10}
    {      \begin{cvitems}        \item {Internship Experience: Interned at UnionPay Technology Clearing House. The team was responsible for using machine learning to predict future clearing transaction volume from historical clearing data, providing data support for future operations and clearing configuration planning. The project used SVM and LSTM algorithms. Also responsible for some clearing transaction data analysis and statistical reporting work.}      \end{cvitems}    }\end{cventries}


\cvsection{Education}
\begin{cventries}  \cventry
    {Ph.D.}
  {East China Normal University}
    {None}
    {2023 - 2027}
    {      \begin{cvitems}        \item {Major: Electronics and Information Technology}      \end{cvitems}    }  \cventry
    {Master}
  {Nanjing University of Aeronautics and Astronautics}
    {None}
    {2014 - 2017}
    {      \begin{cvitems}        \item {Major: Electronics and Communication Engineering}        \item {National Scholarship}        \item {First Prize in National Graduate Mathematical Modeling Contest}      \end{cvitems}    }  \cventry
    {Bachelor}
  {Nanjing University of Aeronautics and Astronautics}
    {None}
    {2010 - 2014}
    {      \begin{cvitems}        \item {Major: Information Engineering}        \item {First Prize in Mathematical Contest in Modeling (MCM)}      \end{cvitems}    }\end{cventries}


%-------------------------------------------------------------------------------
\end{document}
